### 2014-11-07 docs/ms.Rmd
Finalised writing of results with updated dataset from Tom and added the figure

Analysis varied across studies but, overall `r analysisType[1]` analyzed their data by generating colormetric (brightness, hue, chroma) variables whereas `r analysisType[4]` used visual models, `r analysisType[2]` used multiple analysis types (e.g. visual model and colourmetric) and `r analysisType[3]` did other forms of analysis (e.g. RGB, PCA's, GLMMs etc.). Of the studies quantifying colour using spectral reflectance curves `r analysisTypeSpec[1]` used colormetric measures, `r analysisTypeSpec[2]` used multiple analyses, `r analysisTypeSpec[4]` used visual models and `r analysisTypeSpec[3]` used other forms of analysis. Studies using colormetric measurements defined their measure of brightness, hue and/or chroma in `r round(col_def, digits = 2)`% of the studies. Of the studies analysing their data using visual models, `r round(prop_vismod, digits = 2)`% reported the type of visual model they used while only `r round(prop_irrad, digits =2)`%  reported the type of irradiance, `r round(prop_spvismod, digits = 2)`% reported the species used in their visual model and `r round(propvis_mod_param, digits = 2)`% made explicit mention of the parameters they used (i.e. cone densities, neural vs quantum catchs etc.) in their methods.

>>>>

Analysis varied across studies but, overall `r analysisType[1]` analyzed their data by generating colormetric (brightness, hue, chroma) variables whereas `r analysisType[4]` used visual models, `r analysisType[2]` used multiple analysis types (e.g. visual model and colourmetric) and `r analysisType[3]` did other forms of analysis (e.g. RGB, PCA's, GLMMs etc.). Of the studies quantifying colour using spectral reflectance curves `r analysisTypeSpec[1]` used colormetric measures, `r analysisTypeSpec[2]` used multiple analyses, `r analysisTypeSpec[4]` used visual models and `r analysisTypeSpec[3]` used other forms of analysis. Studies using colormetric measurements defined their measure of brightness, hue and/or chroma in `r round(col_def, digits = 2)`% of the studies.

Most studies using visual models analysed their data using receptor noise models (`r vismod_type[3]` of `r sum(vismod_type)` studies) while others used hexagon (`r vismod_type[1]` studies) or tcs (`r vismod_type[4]` studies). Case specific models were used in `r vismod_type[2]` cases. Overall, `r round(prop_irrad, digits =2)`% reported the type of irradiance, `r round(prop_spvismod, digits = 2)`% the species used in their visual model and `r round(propvis_mod_param, digits = 2)`% made explicit mention of the parameters they used (i.e. cone densities, neural vs quantum catchs etc.) in their methods. The background used in visual models was reported `r round(prop_bkg, digits = 2)`% of the time. The type of visual noise authors assumed was reported in `r round(prop_noise, digits = 2)`% of the studies. In addition, explicit mention of the type of quantum catche (`r round(prop_qcatch, digits = 2)`%) or whether photoreceptor adaptation (`r round(prop_adap, digits = 2)`%) was accounted for in visual models was not common.

While some of the values reported above seem alarming, it is important to note that papers often made reference to previous work for various methods (`r round(ref_stud, digits = 2)`%) and so these figures are slightly liberal given that referenced work may have comprehensively covered some of these criteria. Despite this, many of the studies that did not reference previous work were lacking in their reporting of many aspects of our criteria suggesting the need for more comprehensive reporting of data collection and analysis methods within studies.

```{r, barplot, eval = TRUE, echo = FALSE, fig.ext = "pdf", fig.cap = "Figure 1"}

par(mfrow=c(1,2))
props   <- c(specModel, camModel, specLight, CamLight, drk_std, white_stdspec, specAVG, camAVG)
N_props <- c((specs+both), (cam+both), length(DatSpec$light_source), length(DatCam$light_source), length(DatSpec$dark_std), length(DatSpec$white_stdspec), length(DatSpec$specpix_avg), length(DatCam$specpix_avg))

names   <- c("Spec", "Cam", "Spec L", "Pix Avg"," Cam L"," Wt Std", "Spec Avg", "Drk Std")
dat     <- t(arrange(data.frame(props, N_props), props, decreasing = TRUE))
colnames(dat) <- names

barplot(dat[1,], ylim = c(0,100), ylab = "Percentage of studies reporting criteria", xlab = "Criteria", col = "gray", space = 0.30, cex.names = 0.72, mgp = c(2.5,0.5,0), cex.axis = 1.2, cex.lab = 1.5) -> bp.out
abline(h = 0, lwd = 2)
text(dat[2,], x = bp.out, y = 98)
text(paste(round(dat[1,], digits = 0), "%", sep = ""), x = bp.out, y = round(dat[1,], digits = 0)*0.5)
mtext("a)", adj = -0.10, padj = -1, cex = 2)

props_analy   <- c(prop_irrad, prop_spvismod, propvis_mod_param, prop_adap, prop_qcatch, prop_bkg, prop_noise)

N_props_analy <- c(length(DatSpec$irrad_type[! is.na(DatSpec$irrad_type)]), length(DatSpec$vis_mod_sp[! is.na(DatSpec$vis_mod_sp)]), length(DatSpec$vis_mod_param[! is.na(DatSpec$vis_mod_param)]), length(DatSpec$vis_mod_adapt[! is.na(DatSpec$vis_mod_adapt)]), length(DatSpec$vis_mod_qcatch[! is.na(DatSpec$vis_mod_qcatch)]), length(DatSpec$vis_mod_bkg[! is.na(DatSpec$vis_mod_bkg)]), length(DatSpec$vis_mod_noise_type[! is.na(DatSpec$vis_mod_noise_type)]))

dat_analy     <- t(arrange(data.frame(props_analy, N_props_analy), props_analy, decreasing = TRUE))

names_analy   <- c("SpRep", "Bkg", "Irrad", "Qcatch","Noise"," ChrAdapt", "ModPara")
colnames(dat_analy) <- names_analy

barplot(dat_analy[1,], ylim = c(0,100), ylab = "Percentage of studies reporting criteria", xlab = "Criteria", col = "gray", space = 0.30, cex.names = 0.72, mgp = c(2.5,0.5,0), cex.axis = 1.2, cex.lab = 1.5) -> bp.out
abline(h = 0, lwd = 2)
text(dat_analy[2,], x = bp.out, y = 98)
text(paste(round(dat_analy[1,], digits = 0), "%", sep = ""), x = bp.out, y = round(dat_analy[1,], digits = 0)*0.5)
mtext("b)", adj = -0.10, padj = -1, cex = 2)

```
